On the Cram\'{e}r-Rao bound for polynomial phase signals

### 2013-02-08 paper.tex
mved stuff
added to elsev

%\documentclass[draftcls, onecolumn, 11pt]{../../bib/IEEEtran}
\documentclass[journal,10pt]{IEEEtran}

@@

@@

@@

\author{Robby McKilliam and Andr\'{e} Pollok%
\thanks{Supported under the Australian Government's Australian Space Research Program.
Robby McKilliam and Andr\'{e} Pollok are with the Institute for Telecommunications Research, The University of South Australia, SA, 5095}
}
% The paper headers
\markboth{Robby McKilliam and Andre Pollock, On the Cram\'{e}r-Rao bound for polynomial phase signals}%
{DRAFT \today}

% make the title area
\maketitle

\begin{abstract}
Polynomial-phase signals have applications including radar, sonar, geophysics, and radio communication.  Of practical importance is the estimation of the parameters of a polynomial phase signal from a sequence of noisy observations.  
%Assuming that the noise is additive and Gaussian,  Peleg and Porat approximated the Cram\'{e}r-Rao bound for this estimation problem.  The approximation is accurate when the number of observations is sufficiently larger than the order of the polynomial phase signal.  
We derive closed form formulae for the Cram\'{e}r-Rao  lower bounds of these parameters under the assumption that the noise is additive white and Gaussian.  This is achieved by making use of a family of orthogonal polynomials.
\end{abstract}

\begin{IEEEkeywords}
Polynomial-phase signals, Cram\'{e}r-Rao bound.
\end{IEEEkeywords}

@@

%\bibliographystyle{IEEEbib}
\small 
\bibliography{bib}

>>>>

%\documentclass[preprint,10pt]{elsarticle}
%\documentclass[review]{elsarticle}
\documentclass[5p]{elsarticle}

@@

\journal{Signal Processing}

@@

\begin{frontmatter}

@@

\author{Robby McKilliam} 
\author{Andr\'{e} Pollok}
\address{Institute for Telecommunications Research, The University of South Australia, SA, 5095}
\fntext[asrp]{Supported under the Australian Government's Australian Space Research Program.}

\begin{abstract}
Polynomial-phase signals have applications including radar, sonar, geophysics, and radio communication.  Of practical importance is the estimation of the parameters of a polynomial phase signal from a sequence of noisy observations.  
Assuming that the noise is additive and Gaussian, the direct evaluation of the Cram\'{e}r-Rao lower bound for this estimation problem involves evaluating the inverse of a matrix.  Computing this inverse is numerically difficult for polynomial phase signal of large order.  By making use of a family of orthogonal polynomials, we derive formulae for the Cram\'{e}r-Rao lower bounds that are numerically stable and easy to compute.
\end{abstract}

\begin{keyword}
Polynomial-phase signals, Cram\'{e}r-Rao bound.
\end{keyword}

\end{frontmatter}

@@

\bibliographystyle{elsarticle-num}
%\small 
\bibliography{bib}
